Analyzing Build Logs Using Programming by Example

### 2019-06-16 paper/paper.tex
correct introduction + rw, try to write ie/ir part, evaluation draft, research flow image

\secfunc{section function - secfunc} \\
\mention{things to mention / reference - mention} \\
\plan{what to write here - plan} \\
\bp{actual bullet points - bp} \\
\draft{final text drafty - draft} \\
\review{final text review ready - review} \\
\todo{ToDo - todo} \\

@@

\draft{Fixing a broken continuous integration build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.
During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to recover the relevant information from between many uninteresting other lines.

One way to support them would be to extract the desired Information and present it in and present it in a structured way.
Usually such functionality is realized by tools that employ handrcrafted regular expressions to find the desired text parts within the build log.
However, creating these regular expressions is a tedious and mentally complicated work, especially when they have to be maintained some months in the future \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers \textemdash.
Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.

We implemented \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples using the Microsoft PROSE library~\cite{le2014flashextract:}.
After collecting a diverse set of build logs from Travis CI we designed a meta-model of the contained information.
Our evaluation of ALBE showed that it is able to define extractinos for various desired informations, that it shortens development time in comparison to manual regex cnosturction and ...
}

@@

\draft{
The software engineering research community started to look into build logs as continuous integration becomes a vital part of a modern software engineering process. Reserachers have analyzed industrial and open source logs for failure reasons and their impact on development.

Seo et al.~\cite{seo2014programmers} found that at google few error types such as dependency mismatches are the most prominent cause of build failures and most failures are resolved within two builds. Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in java to industrial ones. They determined that testing failures outweigh compilation errors and that open source bulids fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects. Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds. They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being pretested before sent to the CI server.

@@

\subsection{Tool}

\draft{
Vassallo et al.~\cite{vassallo2018un-break} also made it their task to shortening the time it takes developers to understand builogs. They summarize relevant information in Java/maven buildlogs and augment them with links to related stack overflow posts. They observed that highlighting the locality and context of an issue is helpful to programmers. We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.

Amar et al.~\mention{cite icse paper} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs. Further they employ information retrieval techniques to identify the lines most likely hinting at the cause of the error. In contrast to that, instead of comparing whole our tool ALBE extracts specific parts of the build logs. As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
}

@@

\plan{
explain / define information retrieval \bp{matching text piece to similar (maybe labeled) ones in order to identify ... topic}

apply to our use case: paragraph/passage retrieval \bp{for our use case this could be done by slicing the builog into lines similar as \mention{paper about passage retrieval} does it with ...}

define information extraction \bp{pulling specific information out of text is called information extraction}

short: difference to retrieval, fuzzyness

\bp{in our work we decided to focus on the extraction of exact information from build logs}
}

\draft{
Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft PROgram Synthesis using Examples} (PROSE) framework. It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples. Users can extract multiple fields and structure them with hierarchy and sequence. FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.

@@

\draft{
Software build logs are inherently semi-structured data. \todo{explain the different charactersitics and relate to buildlogs}
Serge Abiteboul characterized semi-structured data as having an irregular, implicit, partial and rapidly evolving texture.
}

\plan{characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access \cite{abiteboul1997querying}}

@@

@@

\draft{Obtaining the newes logs from them would entail sampling mostly logs of succeeding builds as the distribution of build states on a Travis CI repository is highly skewed towards successfull builds~\cite{beller2017oops}. Therefore we stratify our collection of logs and select an equal amount of logs from each type of Travis CI build status.}
}

@@

queryed ghtorrent dataset from the first of april 2018 through google bigquery

@@

downloaded logs throuh Travis Rest API \todo{look up version}
}

\plan{describe process of collecting buildlog files, sampling}

\bp{querying ghtorrent and travis api with (insert fancy name for data collection tool) for x buildlogs of each status of the top-watched repositories on github that also use travis ci}

\subsection{Meta-Model}
\bp{through manual examination of y of the buildlogs we collected designed a metamodell  of the contained/extractable/useful/interesting information}

\todo{figure with metamodel}

@@

\subsection{Our Tool}
\plan{interaction and usage and output of tool, maybe integration possibilities}

\plan{capabilities: give example extractions \& limitations}

\plan{necessary or interesting implementation details}

@@

\plan{achieved accuracy, samples needed for same accuracy as related tools (travistorrent), aging of learned programs with newer data}

>>>>

\secfunc{section function - \textbackslash secfunc} \\
\mention{things to mention / reference - \textbackslash mention} \\
\plan{what to write here - \textbackslash plan} \\
\bp{actual bullet points - \textbackslash bp} \\
\draft{final text drafty - \textbackslash draft} \\
\review{final text review ready - \textbackslash review} \\
\todo{ToDo - \textbackslash todo} \\

@@

\review{Fixing a broken continuous integration (CI) build has a high priority for developers~\cite{vassallo2018un-break}, therefore decreasing the time until the green build state is restored improves the overall productivity of developers.
During this assignment an engineer spends most of their time reading very long and verbose build logs, trying to recover the relevant information from between many uninteresting other lines.

One way to support them would be to extract the desired information and present it in a structured way.
Usually such functionality is realized by tools that employ handcrafted regular expressions to find the desired text parts within the build log.
However, creating these regular expressions is tedious and mentally complicated task, especially when they have to be maintained some months in the future \textemdash \ reunderstanding old regular expressions is known to be a dreading task for developers \textemdash.
Our goal is it to take this burden of programmers by enabling them to define extraction programs through simply giving examples of the desired extractions.

We implemented \todo{<toolname, ALBE?, Analyzing Logs By Example>}, a prototype for defining text extractions from build logs through examples.
After collecting a diverse set of build logs from Travis CI we designed a meta-model of the contained information.
Our evaluation of ALBE showed that it is able to define extractions for various desired informations, that it shortens development time in comparison to manual regular expression construction and ...
}

\todo{Research Questions!}

\bp{ RQ1: how many and which kind of samples does pbe need to be competitive with existing methods? }

\bp{ can pbe extraction replace or even exceed existing methods for our use case? }

\bp{ What are the limitations of extractions? (only interesting when specified with PROSE library..)}

\bp{ Adjustements / Improvements to PROSE for extracting specifically from build logs }

@@

\review{
The software engineering research community started to look into build logs as continuous integration becomes a vital part of a modern software engineering process. Researchers have analyzed industrial and open source logs for failure reasons and their impact on development.

Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at google. In addition most failures are resolved within two builds. Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones. They determined that testing failures outweigh compilation errors. Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects. Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds. They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.

@@

\subsection{Tools}

\review{
Vassallo et al.~\cite{vassallo2018un-break} also made it their task to shorten the time it takes developers to understand build logs. They summarize relevant information in Java/maven build logs and augment them with links to related stack overflow posts. They observed that highlighting the locality and context of an issue is helpful to programmers. We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.

Amar et al.~\cite{amar2019mining} reduced the lines of a log to be inspected by the engineer through removing lines that appear both in passing and failing build logs. Further they employ information retrieval techniques to identify the lines most likely hinting at the cause of the error. In contrast to that, our tool ALBE extracts specific parts of the build logs. As this is mostly dependent on the implicit reoccurring structure within the logs we operate on the full log output.
}

@@

\draft{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources. Usually this is done by removing irrelevant terms and stop words, stemming and weighting the remaining words before comparing the similar of those weights against other text parts.~\cite{panichella2016parameterizing} For our use case this could be applied by slicing the build logs into lines or small sections. Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.

In our work we focus on a more precise form of information extraction where we try to obtain a specific detail from a build log instead of retrieving the general idea of a document part.}

\review{
Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework. It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples. Users can extract multiple fields and structure them with hierarchy and sequence. FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.

@@

\draft{
Software build logs are inherently semi-structured data. \todo{explain the different characteristics and relate to build logs}
Serge Abiteboul~\cite{abiteboul1997querying} characterized semi-structured data as having an irregular, implicit, partial and rapidly evolving texture.
}

@@

\begin{figure}
	\includegraphics[width=0.5\textwidth, trim={0.5cm 5cm 3cm 2cm}, clip]{img/flow-of-research.pdf}
	\caption{Flow of Research}
\end{figure}

@@

\draft{Obtaining the newest logs from them would entail sampling mostly logs of succeeding builds as the distribution of build states on a Travis CI repository is highly skewed towards successful builds~\cite{beller2017oops}. Therefore we stratify our collection of logs and select an equal amount of logs from each type of Travis CI build status.}
}

@@

queryed ghtorrent dataset from the first of April 2018 through google BigQuery

@@

downloaded logs through Travis Rest API \todo{look up version}
}

\subsection{Meta-Model}
\bp{through manual examination of y of the build logs we collected designed a meta-model  of the contained/extractable/useful/interesting information}

\todo{figure with meta-model}
\begin{figure}
	\includegraphics[width=0.5\textwidth, trim={0.5cm 4cm 3cm 0.5cm}, clip]{img/meta-model.pdf}
	\caption{Meta-Model}
\end{figure}

@@

\subsection{Our Tool: ALBE \textemdash \ Analyzing Logs By Example}

\plan{
techstacky: C\#, dot net core, Microsoft PROSE library specifically their TextExtraction DSL

samples \& learning: labeled data is in xml files, parsed (and shuffled) for examples, program learned for specific instruction

interaction: user can analyze given file with program defined by specific exampleset, if there: describe how to use iteratively growing / shuffling learning process
}

\subsubsection{Capabilities}

\plan{
Example extractions: travis worker, android failure, what we do evaluations on
}

\subsubsection{Limitations}

\plan{
Travis worker both kinds at once, explain PROSE limitations on arbitrary OR regexes

for all limitations: why? and how would we solve that?
}

\subsection{Evaluation}
\bp{
To evaluate our tool we did xyz, we wanted to measure: accuracy of extractions, impression on effort of creating such extraction, compare both to existing methods
}

\subsubsection{Extraction Accuracy}

\bp{we labelled x logs from project y using language z / build tool b. (do for one, maybe extend with further one)

evaluated accuracy \todo{<define accuracy for us>} with growing number of 
\begin{itemize}
	\item random selected
	\item chronologically sampled
	\item hand selected 
\end{itemize}
samples.
}

\subsubsection{Compare to Traditional Methods}
\paragraph{TravisTorrent}
\bp{Beller et al. \mention{cite correct travistorrent paper} reported on manually constructing a parser with regular expressions for ruby \& Java and common build tools / output formats there, they can extract \todo{<explain there extractions, with example necessary?}

android-failure example: decided not to implement as to complicated \todo{<- that kind of already belongs into results, how do we describe the \emph{method} of this comparison accurately??}
}

\paragraph{Manual Regex Construction}
\plan{
for something where I did not look at the synthesized program

alternative: small study with other developers on manual vs. pbe extraction
}

\paragraph{IR paragraph stuff}
\plan{
maybe simple setup with lines implementing vector comparison on keywords ourselves -> how can we reuse the labeling for the c\# tool?
}

\paragraph{Keyword search}
\plan{
either: we give a list of keywords generally associated with the thing we want to extract (e.g. failure/error/..) -> write nicely how we brainstormed that

or: small study of what developers would search for (maybe literature already did that?)

or: relate to samples? search for already seen words from last failure
}

@@

\plan{graphs!, achieved accuracy, samples needed for same accuracy as related tools (travistorrent), aging of learned programs with newer data}
